---
title: "Google Analytics"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r, echo = FALSE, hide = TRUE, message = FALSE}

install.packages("maps")

library(lubridate)
library(tidyverse)
library(maps)
library(viridis)

root_dir <- rprojroot::find_root(rprojroot::has_dir(".git"))
yaml <- yaml::read_yaml(file.path(root_dir, "_config_automation.yml"))

## For google analytics
ga_metrics <- readr::read_tsv(file.path("metricminer_data", "ga", "ga_metrics.tsv"))
ga_metric_streams <- readr::read_csv(file.path("metricminer_data", "manual", "ga_report_csv_export.csv"))
ga_dimensions <- readr::read_tsv(file.path("metricminer_data", "ga", "ga_dimensions.tsv"))
ga_link_clicks <- readr::read_tsv(file.path("metricminer_data", "ga", "ga_link_clicks.tsv"))
```

## Engagement statistics

### Case study specific

```{r echo = FALSE, hide = TRUE, message=FALSE, warning = FALSE}
ga_metric_streams %>% 
  filter(str_detect(`Page path and screen class`, "ocs-bp")) %>% 
  filter(!str_detect(`Page path and screen class`, "interactive|html|templates")) %>% 
  select(c(`Page path and screen class`, Views, `Active users`, `Average engagement time per active user`, `Event count`)) %>% 
  pivot_longer(!c(`Page path and screen class`), values_to = "value", names_to = "metric_name") %>%
  ggplot(aes(x = reorder(`Page path and screen class`, value), y = value)) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_minimal() +
  facet_wrap(~metric_name, scales = "free_y") + 
  theme(axis.text.x=element_text(angle=60, hjust=1), 
                 strip.text.x = element_text(size = 8)) +
  xlab("Case study") +
  ylab("")
```

### Main Webpage and Pooled Across Case Studies

```{r echo=FALSE, hide=TRUE, message=FALSE, warning=FALSE, out.width = "100%"}
knitr::kable(ga_metrics)
```

## Web traffic overtime

### Main Open Case Studies Website

```{r echo=FALSE, hide=TRUE, message=FALSE, warning=FALSE, fig.height = 6.20, fig.width = 8.89}
ga_dimensions %>% 
  filter(str_detect(website, "OCS main")) %>%
  filter(!str_detect(fullPageUrl, "/?q=|localhost|.com|rmd_output")) %>%
  mutate(month_year = ym(paste0(year, "-", month))) %>%
  group_by(month_year) %>% 
  count() %>% 
  ggplot(ggplot2::aes(y = n, x = month_year)) + 
  geom_bar(stat = "identity") + 
  scale_x_date(date_labels = "%b %Y") + 
  ylab("OCS Main Website Traffic") +
  xlab("") +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=60, hjust=1))
```

### Case Studies

```{r echo=FALSE, hide=TRUE, message=FALSE, warning=FALSE, fig.height = 5.94, fig.width = 8.91}
ga_dimensions %>%
  filter(!str_detect(website, "OCS main")) %>%
  filter(str_detect(fullPageUrl, "ocs-bp")) %>%
  filter(!str_detect(fullPageUrl, "rsconnect|interactive")) %>%
  mutate(month_year = ym(paste0(year, "-", month)),
    case_study = case_when(str_detect(fullPageUrl, "youth-mental-health") ~ "ocs-bp-youth-mental-health",
                                str_detect(fullPageUrl, "opioid") ~ "ocs-bp-opioid-rural-urban",
                                str_detect(fullPageUrl, "obesity") ~ "ocs-bp-rural-and-urban-obesity",
                                str_detect(fullPageUrl, "vaping") ~ "ocs-bp-vaping-case-study",
                                str_detect(fullPageUrl, "school-shootings") ~ "ocs-bp-school-shootings-dashboard",
                                str_detect(fullPageUrl, "diet") ~ "ocs-bp-diet",
                                str_detect(fullPageUrl, "youth-disconnection") ~ "ocs-bp-youth-disconnection",
                                str_detect(fullPageUrl, "co2-emissions") ~ "ocs-bp-co2-emissions",
                                str_detect(fullPageUrl, "RTC-wrangling") ~ "ocs-bp-RTC-wrangling",
                                str_detect(fullPageUrl, "RTC-analysis") ~ "ocs-bp-RTC_analysis",
                                str_detect(fullPageUrl, "pollution") ~ "ocs-bp-air-pollution")) %>%
  group_by(month_year, case_study) %>% 
  count() %>% 
  ggplot(ggplot2::aes(y = n, x = month_year, fill=case_study)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~case_study) +
  scale_x_date(date_labels = "%b %Y") + 
  ylab("Case Study Website Traffic") +
  xlab("") +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=60, hjust=1), legend.position = "none")
```

### Countries accessing OCS Resources

```{r echo=FALSE, hide=TRUE, message=FALSE, warning=FALSE, fig.width = 12.07, fig.height=6.64}
world_data <- map_data("world")

countries <- ga_dimensions$country %>%
  data.frame() %>% `colnames<-`(c("Country")) %>%
  filter(!Country == "(not set)") %>%
  mutate(Country = recode(Country, "United States" = "USA",
                             "United Kingdom" = "UK",
                        "Türkiye" = "Turkey",
                        "U.S. Virgin Islands" = "Virgin Islands",
                        "Hong Kong" = "China",
                        "Bosnia & Herzegovina" = "Bosnia and Herzegovina",
                        "Congo - Kinshasa" = "Democratic Republic of the Congo",
                        "Czechia" = "Czech Republic",
                        "Eswatini" = "Swaziland",
                        "Macao" = "China",
                        "Myanmar (Burma)" = "Myanmar",
                        "Réunion" = "Reunion"
                        )) 

row_indices_oi <- which(str_detect(countries$Country, "Kitts|Vincent|Trinidad"))
valuesOI <- countries[row_indices_oi,]
countries <- rbind(data.frame(countries[-row_indices_oi, ]) %>% `colnames<-`(c("Country")),
                   data.frame(Country = unlist(valuesOI %>% str_split(" & ")) %>% str_replace(., "St.", "Saint"))
                  )

### Make sure all data has a corresponding entry in the map data
whichDifName <- which(unlist(lapply(1:nrow(countries), function(x) !(countries$Country[x] %in% world_data$region))))

if (!length(whichDifName) > 0){
  print("There are entries in the GA data that don't have corresponding entries in in the world map data")
  knitr::kable(countries$Country[whichDifName])
}

### Count number of entries per country
countries %<>%
  group_by(Country) %>% count()

### Merge with world map data and plot, coloring by number of visits
merged_data <- merge(world_data, countries, by.x = "region", by.y = "Country", all.x = TRUE)

ggplot(merged_data,
       aes(map_id = region)) +
geom_map(data = merged_data,
         map = world_data,
         aes(x = long, y = lat, map_id = region, fill=n)) +
  scale_fill_gradientn(colours=rev(magma(6)))  + 
  labs(fill = "Number of Interactions") +
  theme(panel.background = element_blank(), 
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank())
```

In the above map, gray represents no interaction data for that country.

`r nrow(countries)` countries are represented in the web traffic data. The top countries with over 100 users are below

```{r echo=FALSE, hide=TRUE, message=FALSE, warning=FALSE}
knitr::kable(countries$Country[which(countries$n >= 100)])
```
